### 2021-10-18 docs/manuscript/manuscript.tex
Correct statement of scaling of Turing mechanisms

Despite having only two genes, the regulatory mechanism underlying
the topology 9 generates dynamically more complex expression patterns
compared to other topologies, such as the
I3-FFL; however, and despite the fact that the Gierer-Meinhardt model forms
patterns that scale with tissue size~\cite{shoaf1984}, we found that topology 9
was more sensible to changes in the morphogenetic field size than those
topologies based on I3-FFL (\nameref{S2_Table}),
indicating that the additional regulatory interactions need to be fine-tuned
depending on the number of cells in the field.\\

>>>>

Despite having only two genes, the regulatory mechanism underlying
the topology 9 generates dynamically more complex expression patterns
compared to other topologies, such as the
I3-FFL; however, and despite the fact that the Gierer-Meinhardt model forms
patterns that can scale with tissue size in the presence of external
forcing~\cite{shoaf1984, ishihara_2006}, we found that topology 9
was more sensible to changes in the morphogenetic field size than those
topologies based on I3-FFL (\nameref{S2_Table}),
indicating that the additional regulatory interactions need to be fine-tuned
depending on the number of cells in the field.\\
